How to compute the fusion product of MV cycles in type A

### 2021-03-16 draft.tex
minor fixes and bib adds

We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
\acom{This identification assumes we are taking $\CC$ points of $G$ right? i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?} 
\jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}

@@

\acom{Add $G_1$}

@@

\jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
\acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts, $ \Gr^+$ and ${\Grth}^+$, of the affine Grassmannian and the thick affine Grassmannian, respectively, are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
    % 
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).

@@

The following subsets are indexed by coweights. 
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.

@@

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

    \item To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]

@@

    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
    $$
    \UU^{\mu_1, \mu_2}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).

@@

    $\UU_{0,0}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    
            % \mapsto 
            % \left[\begin{array}{rr}
            %     t^{3} & 0 \\
            %     -A_{12}^2 t - A_{12}^1 & t^{2}
            % \end{array}\right]
    \]
    $\UU^{\mu_1, \mu_2}_\AA$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in BD, FL, MV, AK, BFM.

Interesting combinatorics? Witnessing a product on SSYT.

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$.
        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
        % \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

@@

    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$. We know that \acom{by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on 
    % $ \CC\xt^m / L(0)$ 
    $\cO^m/L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on 
    % $ \CC\xt[t-s]^m / L(s) $ 
    $\cO_s^m/L(s)$ has Jordan type $ \lambda_2$.  Now, the map 
    % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
    $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.   The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$. This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).

@@

    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
    % 
    \end{proof}

\begin{lemma}
    Let $\mu_1,\mu_2 \in P$ and $\mu = \mu_1 + \mu_2$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_{0,\AA}$ lands in $ \cW_\mu$.
\end{lemma}

>>>>

% \acom{Add $G_1$}
\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$. The affine space of $m\times m$ matrices which we denote $ M_m$. The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
% TODO: Thank you - resolved!
% \acom{This identification assumes we are taking $\CC$ points of $G$ right? i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?} 
% \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}

@@

@@

% \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
% \acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
% TODO: Just trying it out

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    % \Gr = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    % \Gr_s = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        % \Grth = 
        % \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    % \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    % \Gr_{0,s} = 
    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts, 
    \[
        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)
    \]
    and
    \[
        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
    \]
    % $ \Gr^+$ and ${\Grth}^+$, 
    of the affine Grassmannian and the thick affine Grassmannian, respectively. %, are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    % $$
    % \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
    % $$
    % 
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).

@@

The following subsets are indexed by coweights. 
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % $$ 
    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    % $$ 
    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ in the proof of \cite[Proposition 3.1.14]{zhu2016introduction}.

@@

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
    % 
    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{But our $A$ is always nilpotent? Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    % S^{\mu_1, \mu_2}_{0,s} = 
    N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

    \item To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]

@@

    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu_1, \mu_2}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu_1, \mu_2}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).

@@

    $\UU_{0,0}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    
            % \mapsto 
            % \left[\begin{array}{rr}
            %     t^{3} & 0 \\
            %     -A_{12}^2 t - A_{12}^1 & t^{2}
            % \end{array}\right]
    \]
    $\UU^{\mu_1, \mu_2}_{0,\AA}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.

Interesting combinatorics? Presumably it is related to Feigin and Loktev's generalized Kostka polynomials? Though Joel says that the product on SSYT that we are witnessing is unlikely to have a combinatorial description.

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$. \acom{vestigial $L_0$}
        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
        % \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

@@

    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$. We know that \acom{Rather than we know, it is by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on 
    % $ \CC\xt^m / L(0)$ 
    $\cO^m/L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on 
    % $ \CC\xt[t-s]^m / L(s) $ 
    $\cO_s^m/L(s)$ has Jordan type $ \lambda_2$.  Now, the map 
    % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
    $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.   The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$. This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i). \acom{is this map $v + L \mapsto v + L(0)$?}

@@

    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
    % 
    \end{proof}
\acom{note-to-self, skipped this; return to it.}

\begin{lemma}
    Let $\mu_1,\mu_2 \in P$ and $\mu = \mu_1 + \mu_2$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_{0,\AA}$ lands in $ \cW_\mu$.
\end{lemma}
\acom{the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too.. Anyway I think that you address this below Joel. Probably it is worth writing out the map just before this first occurence? \textit{is it $(L,s)\mapsto L$?}}
